sem

### 2022-12-29 scripts/workshop/sem.Rmd
Update sem.Rmd

histograms
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(cc))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=Prevalence)) + geom_histogram()
```
plots
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(cc))) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(cc), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
```

@@

>>>>

histograms
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log(cc))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=Prevalence)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(Prevalence+1))) + geom_histogram()

```
plots
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = cc)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=log10(cc), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
```

@@

```{r}
comm_data %<>% filter(MeanWaterTempPredC>0)

cc_temp <- gam(log10(cc) ~ s(MeanWaterTempPredC), data = comm_data)
size_temp <- lm(log10(size) ~ (MeanWaterTempPredC), data = comm_data)
prev_cc <- lm(Prevalence ~ log10(cc) + log10(size), data = comm_data)
prev_temp_cc <- glm(Prevalence ~ log10(cc) + log10(size) + MeanWaterTempPredC, data = comm_data)

summary(cc_temp)
